Missing data: Current practice in football research and recommendations for

### 2020-09-11 paper/paper.Rmd
edit wording.

@@

Missing data are often unavoidable. The reason values go missing, along
with decisions made of how missing data are handled (deleted or
imputed), can have a profound effect on the validity, accuracy and usability 
of a study's results. In this article, we aimed to: estimate
the proportion of studies in football research that included a missing
data statement, highlight several practices to avoid in relation to
missing data, and provide recommendations for exploring, visualising and
reporting missingness. Football related articles, published in 2019 were
studied. A survey of 137 articles, sampled at random, was conducted to
determine whether a missing data statement was included. As expected, the
proportion of studies in football research that included a missing data
statement was low, at only X% (95% confidence interval; X% to X%); suggesting that 
missingness is seldom considered by researchers. It is suspected that this result 
is consistent with practice in the wider sports science literature. We recommend 
researchers describe the number and percentage of missing
values, including when there are no missing values. Exploratory analysis
should be conducted to explore missing values, and visualisations
describing missingness overall should be provided in the paper, or at
least supplementary materials. Missing values should almost always be
imputed, and imputation methods should be explored to ensure they are
appropriately representative.

@@

## Practices to avoid across the analysis pathway

>>>>

Authors: David N Borg(1), Robert Nguyen(2), Nicholas J Tierney(3,4)

@@

Missing data are often unavoidable. The reason values go missing, along
with decisions made of how missing data are handled (deleted or
imputed), can have a profound effect on the validity, accuracy and usability 
of a study's results. In this article, we aimed to: estimate
the proportion of studies in football research that included a missing
data statement, highlight several practices to avoid in relation to
missing data, and provide recommendations for exploring, visualising and
reporting missingness. Football related articles, published in 2019 were
studied. A survey of 136 articles, sampled at random, was conducted to
determine whether a missing data statement was included. As expected, the
proportion of studies in football research that included a missing data
statement was low, at only X% (95% confidence interval; X% to X%); suggesting that 
missingness is seldom considered by researchers. It is suspected that this result 
is consistent with practice in the wider sports science literature. We recommend 
researchers describe the number and percentage of missing
values, including when there are no missing values. Exploratory analysis
should be conducted to explore missing values, and visualisations
describing missingness overall should be provided in the paper, or at
least supplementary materials. Missing values should almost always be
imputed, and imputation methods should be explored to ensure they are
appropriately representative.

@@

## Practices to avoid
